On exponential sums arising from the classical doubling method

### 2025-03-03 paper.tex
Typo
Calvin stuff

\subsubsection{Gauss sum notations}
If $\alpha \colon \multiplicativegroup{\finiteFieldExtension{n}} \to \multiplicativegroup{\cComplex}$ is a character, denote the \emph{Gauss sum} $$\tau\left(\alpha, \fieldCharacter_n\right) = -q^{-\frac{n}{2}}\sum_{x \in \multiplicativegroup{\finiteFieldExtension{n}}} \alpha\left(x\right) \fieldCharacter_n\left(x\right),$$
where $\fieldCharacter_n \colon \finiteFieldExtension{n} \to \multiplicativegroup{\cComplex}$ is given by $\fieldCharacter_n = \fieldCharacter \circ \trace_{\finiteFieldExtension{n} \slash \finiteField}$. If $\chi \colon \multiplicativegroup{\finiteField} \to \multiplicativegroup{\cComplex}$ is a character and if $\alpha$ is as above, denote the \emph{twisted Gauss sum}
$$\tau\left(\alpha \times \chi, \fieldCharacter_n\right) = -q^{-\frac{n}{2}}\sum_{x \in \multiplicativegroup{\finiteFieldExtension{n}}} \alpha\left(x\right) \chi\left( \FieldNorm{n}{1}\left(x\right)\right) \fieldCharacter_n\left(x\right).$$

@@

For a torus theta pair $(T,\theta)$ with associated Frobenius conjugacy classes $w \in W(\mathbb{T})$ and $(s) \subset G^*$ and an embedding $\rho:G^* \to  GL_n$.  Fix a Frobenius stable maximal torus $\mathbb{T}^* \subset G^*$ and a Frobenius stable maximal torus $\mathbb{T} \subset GL_n$ which contains $\rho(\mathbb{T}^*)$. Let $\tilde{T}$ be the torus of $GL_n$ corresponding to the Frobenius conjugacy class of $\rho(w) \in W(\mathbb{T})$ and $\tilde{\theta}$ such that $(\rho(s)) = (s_{\tilde{T},\tilde{\theta}})$. Define
\[
    g_{T,\rho}(\theta,\psi,\chi) := \varepsilon_{\algebraicGroup{
    \tilde{T}}}\sum_{t\in \tilde{T}} \tilde{\theta}(t)\chi(det(t))\psi(tr(t)).
\]
\calivn{check $\epsilon$ factors and Hasse-Davenport} The following lemma shows that this is well defined.
\begin{lemma}
\label{lemma:gl_invariance}
\begin{enumerate}[(i)]
	\item In the case $G = GL_n$ and $\rho$ is the standard representation, $g_{T,\rho}(\theta,\psi,\chi)$ depends only on the semisimple conjugacy class of $(s)$.
	\item $g_{T,\rho}(\theta,\psi,\chi)$ is well defined i.e. independent of choice of $\mathbb{T}^* \subset G^*$ and $\mathbb{T} \subset GL_n$.
\end{enumerate}
\end{lemma}
\begin{proof}
(i) In this case when $T = \Pi_{i} \mathbb{F}^{n_i}$ and $\theta = \Pi_{i} \alpha_i$, we recover the Gauss sum
\[
	g_{T,\rho}(\theta,\psi,\chi)  = \varepsilon_{\algebraicGroup{T}} \Pi_i \tau(\alpha_i \times (\chi\circ Nm),\psi) .
\]
By by the Hasse-Davenport relation depends only on the geometric conjugacy class of $(T,\theta)$ hence the semisimple conjugacy class of $(s_{T,\theta})$ \calvin{maybe write more or less?}. 
\\
(ii) For a Frobenius stable semisimple conjugacy class $(s)$ in $GL_n$ in $GL_n$, we define
\[
	g_{(s)}(\psi,\chi) := g_{T,\rho}(\theta,\psi,\chi) \textnormal{ for some } (T,\theta) \textnormal{ such that } (s_{T,\theta}) = (s)
\]
By (i) this is well defined. Then
\[
	g_{T,\rho}(\theta,\psi,\chi)  = g_{(\rho(s_{T,\theta}))}(\psi,\chi)
\]
which is independent of of choice of $\mathbb{T}^* \subset G^*$ and $\mathbb{T} \subset GL_n$.
\end{proof}

@@

\subsubsection{Invariance under geometric conjugacy in Theorem \ref{thm:thm:computation-of-doubling-gauss-sum-scalar-for-deligne-lusztig-characters}}
The main result of this subsection is 
\begin{theorem}
\label{thm:indep_geo_conj}
	$\frac{\dblVirtualGaussSumScalar{R_{T, \theta}}{\chi}}{R_{T,\theta}(1)}$ only depends on the geometric conjugacy class of $(T,\theta)$.
\end{theorem}

The idea of the proof is that the formula from Theorem \ref{thm:thm:computation-of-doubling-gauss-sum-scalar-for-deligne-lusztig-characters} relates $\dblVirtualGaussSumScalar{R_{T, \theta}}{\chi}/R_{T,\theta}(1)$ to $g_{T,\rho}(\theta,\psi,\chi)$ for an appropriate $\rho$. We will need the following computation:
\begin{lemma}
\label{lem:cochar_computation}
    Define $\phi:(\mathbb{Q}/\mathbb{Z})_{p'}^n \to (\mathbb{Q}/\mathbb{Z})_{p'}^{2n} = X_*(GL_{2n})_{(\mathbb{Q}/\mathbb{Z})_{p'}}$ by $\phi(x) = (x,-x)$. We will consider two different Frobeinus actions on these characters:
    \begin{enumerate}
        \item When $F$ acts by trivially on both, $x_{\mathbb{F}_n^\times \times \mathbb{F}_n^\times,\alpha \times \alpha^{-1}} = \phi(x_{\mathbb{F}_n,\alpha})$
        \item When $F$ acts by $-1$ on the domain and by $\begin{pmatrix}
            0 & 1 \\
            1 & 0\end{pmatrix}$ on the codomain, $x_{\mathbb{F}_{2n}^\times,\theta'}=\phi(x_{(\mathbb{F}_{2n})^{Nm=1},\theta})$ where $\theta'(t) = \theta(t^{1-q^n})$
    \end{enumerate}
\end{lemma}
\begin{proof}
Recall that $x_{T,\theta}$ is defined by for sufficiently large $m$ with $\zeta_m = 1/(q^m-1)$ under the fixed identification $\overline{\mathbb{F}}^\times \cong (\mathbb{Q}/\mathbb{Z})_{p'}$
\[
    exp(\langle x_{T,\theta},y\rangle) = \theta(y(N_{T(\mathbb{F}_m):T(\mathbb{F})}(y(\zeta_m))).
\]
Thus the result follows from the computations:\\
(i)
\begin{align*}
    exp(\langle\phi(x_{\mathbb{F}_n,\alpha}),(y_1,y_2)\rangle) &= exp(\langle x_{\mathbb{F}_n,\alpha},\phi^*(y_1,y_2)\rangle) \\
    &= \alpha\left(Nm_{mn:n}(y_1(\zeta_{mn})\right) \alpha\left(Nm_{mn:n}(y_2(\zeta_{mn})\right)^{-1} \\
    &= \left(\alpha\times\alpha^{-1}\right)\left(Nm_{mn:n}((y_1,y_2)(\zeta_{mn}))\right)
\end{align*}
(ii)
\begin{align*}
    exp(\langle\phi(x_{(\mathbb{F}_{2n})^{Nm=1},\theta}),(y_1,y_2)\rangle) &= exp(\langle x_{(\mathbb{F}_{2n})^{Nm=1},\theta},\phi^*(y_1,y_2)\rangle) \\
    &= \theta\left(\frac{Nm_{2mn:2n}(y_1(\zeta_{2mn})}{Nm_{2mn:2n}(y_1(\zeta_{2mn})^{q^n}}\right) \theta\left(\frac{Nm_{2mn:2n}(y_2(\zeta_{2mn})}{Nm_{2mn:2n}(y_2(\zeta_{2mn})^{q^n}}\right)^{-1} \\
    &= \theta'\left(Nm_{2mn:2n}((y_1,y_2)(\zeta_{mn}))\right)
\end{align*}
\end{proof}

Now we fix representations $\rho$ of the dual groups:
\begin{center}
\begin{tabular}{ c c}
 Group & Dual group representations $\rho$ \\ 
 $Sp(2n)$ &$SO(2n+1) \to GL(2n+1)$\\  
 $GSp(2n)$  &$GSpin(2n+1) \to GL(2n+1)$ \\
 $SO(2n)$ &$SO(2n) \to GL(2n)$ \\
 $GO(2n)$ & ? \\
 $SO(2n+1)$ &$Sp(2n) \to GL(2n)$ \\
 $GO(2n+1)$ & ? \\ 
  $U(n)$  & $U(n) \to GL(2n)$  
\end{tabular}
\end{center}
Note that in the $SO$ and $GSO$ case, the map $\rho$ sends the split torus of $G^*$ into the split torus of $GL(2n)$ and the induced map of cocharacters sends $x \mapsto (x,-x)$. In the $Sp,GSp$ cases the map is similar: the induced map of cocharacters sends $x \mapsto (x,1,-x)$. In the unitary case, the torus whose $\mathbb{F}$ points are $(\mathbb{F}_2^{Nm=1})^n \subset G^*(\mathbb{F})$ includes into the torus in $GL(2n)$ whose $\mathbb{F}$ points are $(\mathbb{F}_2^\times)^n$ and the induced map of cocharacters is $(x_1,x_2, \hdots, x_n) \mapsto (x_1,-x_1,x_2,-x_2, \hdots ,x_n,-x_n)$. In all these cases we can apply lemma \ref{lem:cochar_computation}:

\begin{proof}[Proof of theorem \ref{thm:indep_geo_conj}] Let $T$ be a torus in $G$ and suppose $T \cong \prod_{j=1}^r \multiplicativegroup{\finiteFieldExtension{k_j}} \times \prod_{i=1}^s \finiteFieldExtension{2m_i}^1$. We compute $g_{T,\rho}(\theta,\psi,\chi)$ using the the split torus $\mathbb{T}^*$ in $G^*$ including into the split torus $\mathbb{T}'$ in $GL$ in the non unitary case and in the unitary case we use the tori $\mathbb{T}^*$ whose $\mathbb{F}$ points are $(\mathbb{F}_2^{Nm=1})^n \subset G^*(\mathbb{F})$ includes into the torus $\mathbb{T}'$ in $GL(2n)$ whose $\mathbb{F}$ points are $(\mathbb{F}_2^\times)^n$. We then define $\tilde{T}$ as the $\mathbb{F}$-rational torus corresponding to the Frobenius stable Weyl group orbit of $\rho(w)$ inside $W(\mathbb{T}')$ where $(w)$ inside $W(\mathbb{T}^*)$ is the Frobenius stable Weyl group orbit associated to $T$. Lemma \ref{lem:cochar_computation} above implies that
\[
g_{T,\rho}(\theta,\psi,\chi)= \varepsilon_{\algebraicGroup{T}}\varepsilon_{\algebraicGroup{\tilde{T}}}g_{T}(\theta,\psi,\chi) \cdot \begin{cases}
        1  & G \neq Sp, GSp\\
        \tau(1,\psi_1) & G = Sp \textnormal{ or } GSp
    \end{cases}
\]
where $g_T(\theta,\psi,\chi)$ is the expression from theorem \ref{thm:computation-of-doubling-gauss-sum-scalar-for-deligne-lusztig-characters}. \calvin{how does $\epsilon$ depend on $w$? Is the product always one?}.
Corollary \ref{cor:geoconj} then implies that $g_T(\theta,\psi,\chi)$ only depends on the geometric conjugacy class of $(T,\theta)$. Now the formula for $\dblVirtualGaussSumScalar{R_{T, \theta}}{\chi}$ in theorem \ref{thm:computation-of-doubling-gauss-sum-scalar-for-deligne-lusztig-characters} finishes the proof.
\begin{comment}
We will have to treat the unitary group case seperatedly. First for the non-unitary group case:\\

>>>>

\subsubsection{Gauss sum notations}
If $\alpha \colon \multiplicativegroup{\finiteFieldExtension{n}} \to \multiplicativegroup{\cComplex}$ is a character, denote the \emph{Gauss sum} $$\tau\left(\alpha, \fieldCharacter_n\right) = -q^{-\frac{n}{2}}\sum_{x \in \multiplicativegroup{\finiteFieldExtension{n}}} \alpha\left(x\right) \fieldCharacter_n\left(x\right),$$
where $\fieldCharacter_n \colon \finiteFieldExtension{n} \to \multiplicativegroup{\cComplex}$ is given by $\fieldCharacter_n = \fieldCharacter_{\finiteField} \circ \trace_{\finiteFieldExtension{n} \slash \finiteField}$. If $\chi \colon \multiplicativegroup{\finiteField} \to \multiplicativegroup{\cComplex}$ is a character and if $\alpha$ is as above, denote the \emph{twisted Gauss sum}
$$\tau\left(\alpha \times \chi, \fieldCharacter_n\right) = -q^{-\frac{n}{2}}\sum_{x \in \multiplicativegroup{\finiteFieldExtension{n}}} \alpha\left(x\right) \chi\left( \FieldNorm{n}{1}\left(x\right)\right) \fieldCharacter_n\left(x\right).$$

@@

\subsubsection{Invariance under geometric conjugacy}
\calvin{todo:type in some motivation for class functions whose product doesn't depend on geometric conjugacy, gamma functions whatever}.

\begin{definition}
	A \emph{stable function} on $G(\mathbb{F})$ is a class function $f$ such that $\sum_{g \in G} f(g)\pi(g)$ is a scalar which only depends on the Lusztig packet for $\pi$. \calvin{FUNCTORIAL TRANSFER FOR REDUCTIVE GROUPS AND CENTRAL
COMPLEXES has this definition}
\end{definition}

A basic example of a class function which doesn't depend of geometric conjugacy 
\begin{proposition}[FIND SOMEWHERE TO CITE or put in appendix]
\label{prop:central_char}
    Any function supported on the center of $G(\mathbb{F})$ is a stable function. \calvin{maybe add in connected group} 
\end{proposition}
\begin{proof}
\calvin{todo. Here is a sketch. Use the definition of RTtheta to show for all torus theta pairs $(T,\theta)$, central element $x$ acts by scalar (in fact the scalar $\theta(x)$). This can also be showed using the character formula plus the ``only one cuspidal'' trick but it is probably overkill. Then if two pairs are conjugate, their hom dimesnion is nonzero, hence $x$ the scalar in both RTThetas} 
\end{proof}

The main result of this subsection is 
\begin{theorem}
\label{thm:indep_geo_conj}
	$\Phi_{\chi}(g)$ is a stable function.
	%Equivalently	$\frac{\dblVirtualGaussSumScalar{R_{T, \theta}}{\chi}}{R_{T,\theta}(1)}$ only depends on the geometric conjugacy class of $(T,\theta)$.
\end{theorem}

In the $GL_n$ case this follows from theorem \ref{thm:gln-doubling-gauss-sum-in-terms-of-kondo} along with \calvin{Hasse-Davenport? Something else?}.

For a torus theta pair $(T,\theta)$ with associated Frobenius conjugacy classes $w \in W(\mathbb{T})$ and $(s) \subset G^*$ and an embedding $\rho:G^* \to  GL_n$.  Fix a Frobenius stable maximal torus $\mathbb{T}^* \subset G^*$ and a Frobenius stable maximal torus $\mathbb{T} \subset GL_n$ which contains $\rho(\mathbb{T}^*)$. Let $\tilde{T}$ be the torus of $GL_n$ corresponding to the Frobenius conjugacy class of $\rho(w) \in W(\mathbb{T})$ and $\tilde{\theta}$ such that $(\rho(s)) = (s_{\tilde{T},\tilde{\theta}})$. Define
\[
    g_{T,\rho}(\theta,\psi,\chi) := \varepsilon_{\algebraicGroup{
    \tilde{T}}}\sum_{t\in \tilde{T}} \tilde{\theta}(t)\chi(det(t))\psi(tr(t)).
\]
The following lemma shows that this is well defined.

\begin{lemma}
\label{lemma:gl_invariance}
\begin{enumerate}[(i)]
	\item In the case $G = GL_n$ and $\rho$ is the standard representation, $g_{T,\rho}(\theta,\psi,\chi)$ depends only on the semisimple conjugacy class of $(s)$.
	\item $g_{T,\rho}(\theta,\psi,\chi)$ is well defined i.e. independent of choice of $\mathbb{T}^* \subset G^*$ and $\mathbb{T} \subset GL_n$.
\end{enumerate}
\end{lemma}
\begin{proof}
(i) In this case when $T = \Pi_{i} \mathbb{F}^{n_i}$ and $\theta = \Pi_{i} \alpha_i$, we recover the Gauss sum
\[
	g_{T,\rho}(\theta,\psi,\chi)  = \Pi_i \tau(\alpha_i \times (\chi\circ Nm),\psi).
\]
By the Hasse-Davenport relation depends only on the geometric conjugacy class of $(T,\theta)$ hence the semisimple conjugacy class of $(s_{T,\theta})$ \calvin{maybe write more or less?}. 
\\
(ii) For a Frobenius stable semisimple conjugacy class $(s)$ in $GL_n$ in $GL_n$, we define
\[
	g_{(s)}(\psi,\chi) := g_{T,\rho}(\theta,\psi,\chi) \textnormal{ for some } (T,\theta) \textnormal{ such that } (s_{T,\theta}) = (s)
\]
By (i) this is well defined. Then
\[
	g_{T,\rho}(\theta,\psi,\chi)  = g_{(\rho(s_{T,\theta}))}(\psi,\chi)
\]
which is independent of of choice of $\mathbb{T}^* \subset G^*$ and $\mathbb{T} \subset GL_n$.
\end{proof}

@@

The idea behind the proof of this theorem \ref{thm:indep_geo_conj} is that the formula from Theorem \ref{thm:computation-of-doubling-gauss-sum-scalar-for-deligne-lusztig-characters} relates $\dblVirtualGaussSumScalar{R_{T, \theta}}{\chi}/R_{T,\theta}(1)$ to $g_{T,\rho}(\theta,\psi,\chi)$ for the appropriate $\rho$ in the table below. 
\begin{center}
\begin{tabular}{ c c}
 Group & Dual group representations $\rho$ \\ 
 $Sp(2n)$ &$SO(2n+1) \to GL(2n+1)$\\  
 $GSp(2n)$  &$GSpin(2n+1) \to GL(2n+1)$ \\
 $SO(2n)$ &$SO(2n) \to GL(2n)$ \\
 $GO(2n)$ & ? \\
 $SO(2n+1)$ &$Sp(2n) \to GL(2n)$ \\
 $GO(2n+1)$ & ? \\ 
  $U(n)$  & $U(n) \to GL(2n)$  
\end{tabular}
\end{center}
Note that in the $SO$ and $GSO$ case, the map $\rho$ sends the split torus of $G^*$ into the split torus of $GL(2n)$ and the induced map of cocharacters sends $x \mapsto (x,-x)$. In the $Sp,GSp$ cases the map is similar: the induced map of cocharacters sends $x \mapsto (x,1,-x)$. In the unitary case, the torus whose $\mathbb{F}$ points are $(\mathbb{F}_2^{Nm=1})^n \subset G^*(\mathbb{F})$ includes into the torus in $GL(2n)$ whose $\mathbb{F}$ points are $(\mathbb{F}_2^\times)^n$ and the induced map of cocharacters is $(x_1,x_2, \hdots, x_n) \mapsto (x_1,-x_1,x_2,-x_2, \hdots ,x_n,-x_n)$.

In particular to analyze $g_{T,\rho}(\theta,\psi,\chi)$ for these $\rho$, we need to understand what torus theta pair of $GL$ corresponds to $\phi((s))$ under a map $\phi(x) = (x,-x)$:
%The following computation in the proof of theorem \ref{thm:indep_geo_conj}.

\begin{lemma}
\label{lem:cochar_computation}
    Define $\phi:(\mathbb{Q}/\mathbb{Z})_{p'}^n \to (\mathbb{Q}/\mathbb{Z})_{p'}^{2n} = X_*(GL_{2n})_{(\mathbb{Q}/\mathbb{Z})_{p'}}$ by $\phi(x) = (x,-x)$. We will consider two different Frobeinus actions on these characters:
    \begin{enumerate}
        \item When $F$ acts by trivially on both, $x_{\mathbb{F}_n^\times \times \mathbb{F}_n^\times,\alpha \times \alpha^{-1}} = \phi(x_{\mathbb{F}_n,\alpha})$
        \item When $F$ acts by $-1$ on the domain and by $\begin{pmatrix}
            0 & 1 \\
            1 & 0\end{pmatrix}$ on the codomain, $x_{\mathbb{F}_{2n}^\times,\theta'}=\phi(x_{(\mathbb{F}_{2n})^{Nm=1},\theta})$ where $\theta'(t) = \theta(t^{1-q^n})$
    \end{enumerate}
\end{lemma}
\begin{proof}
Recall that $x_{T,\theta}$ is defined by for sufficiently large $m$ with $\zeta_m = 1/(q^m-1)$ under the fixed identification $\overline{\mathbb{F}}^\times \cong (\mathbb{Q}/\mathbb{Z})_{p'}$
\[
    exp(\langle x_{T,\theta},y\rangle) = \theta(y(N_{T(\mathbb{F}_m):T(\mathbb{F})}(y(\zeta_m))).
\]
Thus the result follows from the computations:\\
(i)
\begin{align*}
    exp(\langle\phi(x_{\mathbb{F}_n,\alpha}),(y_1,y_2)\rangle) &= exp(\langle x_{\mathbb{F}_n,\alpha},\phi^*(y_1,y_2)\rangle) \\
    &= \alpha\left(Nm_{mn:n}(y_1(\zeta_{mn})\right) \alpha\left(Nm_{mn:n}(y_2(\zeta_{mn})\right)^{-1} \\
    &= \left(\alpha\times\alpha^{-1}\right)\left(Nm_{mn:n}((y_1,y_2)(\zeta_{mn}))\right)
\end{align*}
(ii)
\begin{align*}
    exp(\langle\phi(x_{(\mathbb{F}_{2n})^{Nm=1},\theta}),(y_1,y_2)\rangle) &= exp(\langle x_{(\mathbb{F}_{2n})^{Nm=1},\theta},\phi^*(y_1,y_2)\rangle) \\
    &= \theta\left(\frac{Nm_{2mn:2n}(y_1(\zeta_{2mn})}{Nm_{2mn:2n}(y_1(\zeta_{2mn})^{q^n}}\right) \theta\left(\frac{Nm_{2mn:2n}(y_2(\zeta_{2mn})}{Nm_{2mn:2n}(y_2(\zeta_{2mn})^{q^n}}\right)^{-1} \\
    &= \theta'\left(Nm_{2mn:2n}((y_1,y_2)(\zeta_{mn}))\right)
\end{align*}
\end{proof}

\begin{proof}[Proof of theorem \ref{thm:indep_geo_conj}] 
By theorem \ref{thm:computation-of-doubling-gauss-sum-scalar-for-deligne-lusztig-characters}, it is enough to show that $g_{T}(\chi,\theta,\psi)$ and $\omega_{\pi}(-1) = \theta(-1)$ only depend of the geometric conjugacy of $(T,\theta)$. The latter only depends on geometric conjugacy by proposition \ref{prop:central_char}.\\

Suppose $T \cong \prod_{j=1}^r \multiplicativegroup{\finiteFieldExtension{k_j}} \times \prod_{i=1}^s \finiteFieldExtension{2m_i}^1$. We compute $g_{T,\rho}(\theta,\psi,\chi)$ using the the split torus $\mathbb{T}^*$ in $G^*$ including into the split torus $\mathbb{T}'$ in $GL$ in the non unitary case and in the unitary case we use the tori $\mathbb{T}^*$ whose $\mathbb{F}$ points are $(\mathbb{F}_2^{Nm=1})^n \subset G^*(\mathbb{F})$ includes into the torus $\mathbb{T}'$ in $GL(2n)$ whose $\mathbb{F}$ points are $(\mathbb{F}_2^\times)^n$. We then define $\tilde{T}$ as the $\mathbb{F}$-rational torus corresponding to the Frobenius stable Weyl group orbit of $\rho(w)$ inside $W(\mathbb{T}')$ where $(w)$ inside $W(\mathbb{T}^*)$ is the Frobenius stable Weyl group orbit associated to $T$. Lemma \ref{lem:cochar_computation} above implies that
\[
g_{T,\rho}(\theta,\psi,\chi)= g_{T}(\theta,\psi,\chi) \cdot \begin{cases}
        1  & G \neq Sp, GSp\\
        \tau(1,\psi_1) & G = Sp \textnormal{ or } GSp
    \end{cases}.
\]
Corollary \ref{cor:geoconj} then implies that $g_T(\theta,\psi,\chi)$ only depends on the geometric conjugacy class of $(T,\theta)$. 
\begin{comment}
We will have to treat the unitary group case seperatedly. First for the non-unitary group case:\\
